---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
---



```{r}
CRM_311 <- read.csv("~/Desktop/CRM Cases 2015_2019 Unrestricted.csv", sep = ",", header = TRUE, stringsAsFactors=FALSE)
head(CRM_311, n = 5)
# Number of rows and Number of columns
dim(CRM_311)
table(CRM_311$BRA_PD)
library(ggplot2)
j <- ggplot(CRM_311[!is.na(CRM_311$REASON),], aes(REASON)) + geom_bar(fill = "tan") + theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 9)) + 
  ggtitle("The reasons of request received") + xlab("Reasons")
ggsave("j.png", path = "~/Desktop")

# Names of columns
colnames(CRM_311)
# Checking for NA data and indicating columns which they have NA
colnames(CRM_311)[apply(is.na(CRM_311), 2, any)]
# Checking for columns which all their values are NA
colnames(my_data)[apply(is.na(my_data), 2, any)]
table(CRM_311$SUBJECT)
table(CRM_311$TYPE)
```


```{r}
# Convert to Date format
library(lubridate)  
m <- as.POSIXct(CRM_311$OPEN_DT,format="%Y-%m-%d %H:%M:%S",tz=Sys.timezone())
h <- ymd_hms(CRM_311$OPEN_DT,tz=Sys.timezone())
CRM_311$OPEN_DT <- as.Date(h, format = "%Y-%m-%d %H:%M:%S'")

n <- as.POSIXct(CRM_311$CLOSED_DT,format="%Y-%m-%d %H:%M:%S",tz=Sys.timezone())
c <- ymd_hms(CRM_311$CLOSED_DT,tz=Sys.timezone())
CRM_311$CLOSED_DT <- as.Date(c, format = "%Y-%m-%d %H:%M:%S'")


```

```{r}
CRM_311$weekdays <- weekdays(CRM_311$OPEN_DT)
months2015 <- months(CRM_311$OPEN_DT[year(CRM_311$OPEN_DT) == 2015])
df2015 <- data.frame(table(months2015))
months2016 <- months(CRM_311$OPEN_DT[year(CRM_311$OPEN_DT) == 2016])
table(months2016)
df2016 <- data.frame(table(months2016))
df2 <- data.frame(df2015, df2016)
df2
table(weekdays(CRM_311$OPEN_DT))
table(weekdays(CRM_311$CLOSED_DT))
n <- ggplot(df2, aes(x = months2015, y = Freq, group = 1)) + geom_point(color = "blue") + geom_line(color = "navy") + labs(x = "Months", y = 'Number of calls', title ='Number of received calls in each month') + theme_bw()
ggsave("n.png", path = "~/Desktop")
m <- qplot(weekdays(CRM_311$OPEN_DT), fill = weekdays(CRM_311$OPEN_DT)) + xlab("Weekdays of received calls")
ggsave("m.png", path = "~/Desktop")
```

```{r}
library(ggplot2)

months2015 <- months(rox$OPEN_DT[year(rox$OPEN_DT) == 2015])
df2015 <- data.frame(table(months2015))
months2016 <- months(rox$OPEN_DT[year(rox$OPEN_DT) == 2016])
df2016 <- data.frame(table(months2016))
df2 <- data.frame(df2015, df2016)


months20155 <- months(rox$CLOSED_DT[year(rox$CLOSED_DT) == 2015])
df20155 <- data.frame(table(months20155))
months20166 <- months(rox$CLOSED_DT[year(rox$CLOSED_DT) == 2016])
df20166 <- data.frame(table(months20166))
df22 <- data.frame(df20155, df20166)



dfasli2 <- merge(df2, df22, by.x = 'months2015', by.y = 'months20155', all.x = TRUE, all.yb = TRUE)
dfasli2 
j2 <- dfasli2 %>%
  ggplot(aes(x = months2015, y = dfasli2$Freq.x, group = 1)) + geom_line(color = "brown") + geom_line(y = dfasli2$Freq.y, group = 1) + labs(x = "Months", y = 'Number of calls in Roxbury', title ='Number of received and addressed calls in each month in Roxbury') + theme_bw()
j2
ggsave("j2.png", path = "~/Desktop")
```

```{r}
library(ggplot2)

months2015 <- months(CRM_311$OPEN_DT[year(CRM_311$OPEN_DT) == 2015])
df2015 <- data.frame(table(months2015))
months2016 <- months(CRM_311$OPEN_DT[year(CRM_311$OPEN_DT) == 2016])
df2016 <- data.frame(table(months2016))
df2 <- data.frame(df2015, df2016)


months20155 <- months(CRM_311$CLOSED_DT[year(CRM_311$CLOSED_DT) == 2015])
df20155 <- data.frame(table(months20155))
months20166 <- months(CRM_311$CLOSED_DT[year(CRM_311$CLOSED_DT) == 2016])
df20166 <- data.frame(table(months20166))
df22 <- data.frame(df20155, df20166)

dfasli <- merge(df2, df22, by.x = 'months2015', by.y = 'months20155', all.x = TRUE, all.yb = TRUE)
dfasli 
j <- dfasli %>%
  ggplot(aes(x = months2015, y = dfasli$Freq.x, group = 1)) + geom_line(color = "blue") + geom_line(y = dfasli$Freq.y, group = 1) + labs(x = "Months", y = 'Number of calls in Boston', title ='Number of received and addressed calls in each month in Boston') + theme_bw()
j
ggsave("j.png", path = "~/Desktop")
```





```{r}
sum(table(rox$OPEN_DT))

require(ggplot2)
require(ggmap)
Boston <- get_map(location=c(left = -71.193799, bottom = 42.15, right = -70.985746, top = 42.5))
Bostonmap <- ggmap(Boston)



Bostonmap + stat_density2d(aes(x = X, y = Y, fill = ..level.., alpha = .5), size = .5, bins = 8, data = CRM_311, geom = "polygon")
# Location of each Boston Police Department District in Boston
Bostonmap + geom_density2d(aes(x = X, y = Y), data = CRM_311)+labs(fill='Density of 311 calls in Boston')
```
 
 
```{r}
library(ggplot2)
t <- ggplot(CRM_311[!is.na(CRM_311$SOURCE),], aes(x = "", fill = SOURCE)) + geom_bar(width = 1) + 
  coord_polar (theta="y") + ggtitle("Source of 311 calls") 

ggsave("t.png", path = "~/Desktop")
g1 <- ggplot(CRM_311[!is.na(CRM_311$SUBJECT),]) + geom_bar(aes(x = SUBJECT), fill = "navy", width = 0.5) +
 theme_classic()+ theme(axis.text.x = element_text(angle=90, vjust=0.6, size = 10)) + ggtitle("The department responsible for addressing the request received")
ggsave("g1.png", path = "~/Desktop")
g2 <- ggplot(CRM_311[!is.na(CRM_311$BRA_PD),]) + geom_bar(aes(x = BRA_PD), fill = "pink", width = 0.5) + theme_classic() +
  theme(axis.text.x = element_text(angle=90, vjust=0.6, size = 10)) + ggtitle("The number of 311 calls in each neighborhood") + xlab("Neighborhoods") 
ggsave("g2.png", path = "~/Desktop")

table(CRM_311$REASON)
```


```{r}
library(sqldf)
## Latent variable (1): flexible_host
# Using sqldf command to execute multiple aggregation for flexible_host
b <- sqldf("select BRA_PD as Neighborhood,
                      sum(PUBLIC == 1) as PUBLIC,
                      sum(HOUSING == 1) as HOUSING,
                      sum(UNCIVILUSE == 1) as UNCIVILUSE,
                      sum(BIGBUILD == 1)as BIGBUILD,
                      sum(GRAFFITI == 1) as GRAFFITI,
                      sum(TRASH == 1) as TRASH,
                      sum(PRIVATENEGLECT == 1) as PRIVATENEGLECT,
                      sum(PUBLICDENIG == 1) as PUBLICDENIG,
                      sum(PROBLEM ==1) as PROBLEM
                      from CRM_311
                      where BRA_PD !='NA'
                      group by BRA_PD")



b
write.csv(b,"~/Desktop/nbhd_311.csv", row.names = FALSE)



j <- ggplot(b, aes(Neighborhood, GRAFFITI, fill = as.factor(BIGBUILD))) + geom_bar(stat = "summary", fun.y = "mean") + theme_classic() +theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 10)) + labs(fill = "Big Buildings") + ggtitle("Number of big buildings and graffiti problems at neighborhood level")
j
ggsave("j.png", path = "~/Desktop")
p <- ggplot(b, aes(Neighborhood, HOUSING, size = TRASH)) + geom_point(color = 'red') + theme_classic() + theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 10)) + ggtitle("Number of trash and housing problems at neighborhood level")
ggsave("p.png", path = "~/Desktop")


rox <- CRM_311[CRM_311$BRA_PD == "Roxbury",]
table(rox$REASON)
rox$months2015 <- months(CRM_311$OPEN_DT[year(CRM_311$OPEN_DT) == 2015])

library(ggplot2)

g <- ggplot(rox[!is.na(rox$SOURCE),], aes(x = REASON)) + geom_bar(aes(fill = as.factor(SOURCE))) + theme_bw()+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size = 8)) + labs(fill = "Source") + xlab("Roxbury")+ ggtitle("Reasons and Source of Received calls in Roxbury")
g

ggsave("g.png", path = "~/Desktop")







library(ggdendro)
hc <- hclust(dist(b), "ave")
h <- ggdendrogram(hc, rotate = FALSE, size = 2) 
h

library(tidyverse)
j <- as.data.frame(select(rox, PUBLIC, HOUSING, UNCIVILUSE, BIGBUILD, GRAFFITI, TRASH, PRIVATENEGLECT, PUBLICDENIG,PROBLEM)) 


o2 <- boxplot(j,
main="Subjects of problems that are received in Roxbury",
ylab="Number of 311 calls",
col="orange",
border="brown", las =2,  cex.axis=0.75)
o2
ggsave("o2.png", path = "~/Desktop")

table(CRM_311$BRA_PD)

```

```{r}
b$Neighborhood
library(igraph)
n <- b[b$Neighborhood == "Back Bay/Beacon Hill",]





n
BPD_no.na <- b$Neighborhood[!is.na(b$Neighborhood) == "Back Bay/Beacon Hill",]
Zipcode_no.na <- b$PROBLEM[!is.na(b$PROBLEM)]
nodes_911 <- as.data.frame(c(unique(BPD_no.na), unique(Zipcode_no.na)))
links_911 <- as.data.frame(cbind(BPD_no.na, Zipcode_no.na))
igraph_911 <- graph_from_data_frame(d = links_911, vertices = nodes_911, directed = TRUE)
length(V(igraph_911))
V(igraph_911)[1:13]$color <- "sky blue"
V(igraph_911)[14:37]$color <- "pink"
V(igraph_911)[V(igraph_911)$name == "D4"]$color <- "yellow"
V(igraph_911)[V(igraph_911)$name == "2118"]$color <- "yellow"
V(igraph_911)[V(igraph_911)$name == "2115"]$color <- "yellow"
V(igraph_911)[V(igraph_911)$name == "C10"]$color <- "red"
V(igraph_911)[V(igraph_911)$name == "2125"]$color <- "red"
plot(igraph_911, edge.arrow.size=0.2, edge.color="gray", 
     vertex.label.color="black", vertex.label.font=2, 
     vertex.label.cex=0.8, layout = layout_in_circle)
```

```{r}
library(sf)
# Shapefile of neighborhoods in Boston
nbhd <- st_read(dsn="~/Desktop/Big data for cities/Mapping/bra_planning_districts_2015_zip_pnq/bra_planning_districts_2015_zip_pnq.shp")
# Convert coordinate system
nbhd <- st_transform(nbhd, "+proj=longlat +datum=NAD83 +no_defs")
nbhd_311 <- read.csv("~/Desktop/nbhd_311.csv", sep = ",", header = TRUE, stringsAsFactors=FALSE)
# Merging shapefile and latent variable's file
nbhd <- merge(nbhd, nbhd_311, by.x='PD', by.y = 'Neighborhood',all.x=TRUE)

# Strict Hosts
library(tmap) 
tmap_mode('view')
tm_shape(nbhd) + tm_polygons(c('PROBLEM', 'PUBLIC') , palette=list("Oranges","Reds"), style = "jenks")  + tm_view(alpha = 0.85,view.legend.position = c("right", "bottom")) +  tm_facets(nrow=2,ncol=2)  + tm_layout(title = c("Problem", "Public"))
save_tmap(m2, "CRM.png", width=1920, height=1080, asp=0)
```


```



```{r}

table(CRM_311$REASON)
library(ggplot2)
g1 <- ggplot(CRM_311) + geom_bar(aes(REASON), fill = "tan", width = 0.5) +
  theme(axis.text.x = element_text(angle=90, vjust=0.6)) + ggtitle("The subject of the request received ")
ggsave("g1.png", path = "~/Desktop")


n <- rox[complete.cases(rox$CLOSED_DT),]
m <- qplot(weekdays(n$CLOSED_DT), fill = weekdays(n$CLOSED_DT)) + xlab("The weekdays the case was deemed fully addressed by city services") + labs(fill = "Weekdays of closed case")
m

ggplot(data= rox, aes(x=weekdays(rox$CLOSED_DT))) + 
geom_bar(stat="bin")
last_plot() + coord_polar()
rox$close_time = (as.numeric(rox$CLOSED_DT - rox$OPEN_DT))

ggplot(rox) + geom_bar(aes(close_time), fill = "tan") 



close_time = (as.numeric(CRM_311$CLOSED_DT - CRM_311$OPEN_DT))
close_time

library(dplyr)
dt <- CRM_311 %>% mutate(close_time = (as.numeric(CLOSED_DT - OPEN_DT)), open_year = as.factor(format(CRM_311$OPEN_DT, format = "%Y")), open_month = as.factor(format(CRM_311$OPEN_DT, format = "%m")))
dt$REASON <- as.factor(dt$REASON)


exp_dt <- dt %>% group_by(open_year, open_month) %>% summarize(num_calls = n(), num_reason = n_distinct(REASON), mean_close = round(mean(close_time, na.rm = T),4), median_close = round(median(close_time, na.rm = T),4), max = max(close_time, na.rm = T))
head(exp_dt)

t <- ggplot(exp_dt , aes(y=num_calls/1000, x=open_year, alpha = num_calls, fill = open_month, color = open_month)) + geom_bar(stat="identity") + ggtitle("Number of 311 Requests by year") + xlab("Year") + ylab("Number of Requets (Thousands)")
t


t <- ggplot(exp_dt , aes(y=num_calls/1000, x=open_year, alpha = num_calls, fill = open_month, color = open_month)) + geom_bar(stat="identity") + ggtitle("Number of 311 Requests by year") + xlab("Year") + ylab("Number of Requets (Thousands)")

ggplot(exp_dt, aes(exp_dt$num_reason)) + geom_bar(aes(fill = exp_dt$open_month))

exp_dt$num_reason
```

```{r}


table(CRM_311$BRA_PD)
b <- b[,-1]
as.matrix(b)
row.names(b) <-  c("West Roxbury", "South End", "South Dorchester", "South Boston", "Roxbury", "Roslindale", "North Dorchester", "Mattapan", "Jamaica Plain", "Hyde Park", "Fenway/Kenmore", "East Boston","Charlestown", "Central","Back Bay/Beacon Hill", "Allston/Brighton" )

heatmap(as.matrix(b), scale = 'column', col= heat.colors(256), main = 'heatmap',Rowv = NA, Colv = NA)


```




